Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-15 content/appendix.tex
minor fix
part of proof for lemma 5

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalMeet}}]
  For all $r\in R$ and $m\in R\to2^T$,
\begin{align*}
  &\left(\denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}\right)(m)(r)\\
  &=(\denote{\setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}})(m)(r)\\
  &=(m(r)\cap(I(r)\cup I'(r))\cup U(r)\cup U'(r)\\
  &=(m(r)\cap I(r))\cup U(r)\cup(m(r)\cap I'(r))\cup U'(r)\\
  &=\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)\\
  &=\left(\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}\right)(m)(r).\qedhere
\end{align*}
\end{proof}

@@

We will denote the top element in the environment lattice as
\begin{equation}
  \Omega=\lambda d\,.\,\topcc\,.
\end{equation}

@@

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:sound}}] 
According to~\eqref{eq:ideresult}, we can rewrite~\eqref{eq:transCcDef} as
\begin{equation}\label{eq:transCcResultCc}
  \backCC(\resultIDE(\transCC_R(P)))(n)
  =\{d\,|\,\forall r\in R\,.\,\mvp{\textsf{Env}}(n,\,d))(r)\ne\top_T\}.
\end{equation}
\mtodo{TODO rest of proof!}
Let $\rho=\resultIDE(\transCC_R(P))$. Then
  \begin{align*}
    \backCC(\rho)(n)
    &=D_n^\Subset(\rho)\\
    &=\left\{d'\ |\ 
        d'\in\mvp F(n)\,\wedge\,\forall r\in R:\ \rho(n,\ d')(r)\ne\top_T\right\}.
  \end{align*}
  Since $\mvp F(n)=\bigsqcap_{q\in\ivp(n)}M_F(q)(\varnothing)$, and $p\in\ivp(n)$, it follows that
    \begin{align*}
      d&\in M_F(p)(\varnothing)\\&\subseteq\mvp F(n)\,.
    \end{align*}
  At the same time, for all receivers $r\in R$,
  \begin{align*}
    \rho(n,\,d)(r)
    &=\left(\bigsqcap_{q\in\ivp(n)}\mpddef q d\right)(r)\\
    &=\bigsqcap_{q\in\ivp(n)}\mpddef q d(r)\,.
  \end{align*}
  According to~Lemma~\ref{lem:sound3}, $\mpd(r)\ne\top_T$.
  Since $p\in\ivp(n)$,
  \begin{align*}
    \mpd(r)\subseteq\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)\,.
  \end{align*}
  From $\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)=\rho(n,\,d)(r)$ it follows that
  $\mpd(r)\subseteq\rho(n,\,d)(r)$.
  Therefore, $\rho(n,\,d)(r)\ne\top_T$, and $d\in D_n^\Subset(\rho)=\backCC(\rho)(n)$.
\end{proof}

>>>>

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalMeet}}]
  For all $r\in R$ and $m\in R\to2^T$,
\begin{align*}
  \left(\denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}\right)&(m)(r)\\
  &=(\denote{\setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}})(m)(r)\\
  &=(m(r)\cap(I(r)\cup I'(r))\cup U(r)\cup U'(r)\\
  &=(m(r)\cap I(r))\cup U(r)\cup(m(r)\cap I'(r))\cup U'(r)\\
  &=\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)\\
  &=\left(\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}\right)(m)(r).\qedhere
\end{align*}
\end{proof}

@@

We will denote the top element in the environment lattice as
$\Omega=\lambda d\,.\,\topcc$.

@@

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:sound}}] 
According to~\eqref{eq:ideresult}, we can rewrite~\eqref{eq:transCcDef} as
\begin{align*}\label{eq:transCcResultCc}
  \backCC(\resultIDE(\transCC_R(P)))(n)
  &=\{d'\,|\,\forall r\in R\,.\,\mvp{\textsf{Env}}(n,\,d'))(r)\ne\top_T\}\\
  &=\left\{d'\,|\,\forall r\in R\,.\bigsqcap_{q\in\textsf{VP}(n)}\menv(q)(\Omega)(d')(r)\ne\top_T\right\}\\
  &=\left\{d'\,|\,\forall r\in R\,.\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d'}(r)\ne\top_T\right\}.
\end{align*}
  According to~Lemma~\ref{lem:sound3}, since $d\in M_F(p)(\varnothing)$, then $\mpd(r)\ne\top_T$.
  Since $p\in\ivp(n)$,
  \begin{align*}
    \mpd(r)\subseteq\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)\,.
  \end{align*}
  From $\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)=\rho(n,\,d)(r)$ it follows that
  $\mpd(r)\subseteq\rho(n,\,d)(r)$.
  Therefore, $\rho(n,\,d)(r)\ne\top_T$, and $d\in D_n^\Subset(\rho)=\backCC(\rho)(n)$.
\end{proof}

### 2014-12-15 content/background.tex
part of proof for lemma 5

The output of the IDE algorithm is, for each node $n$ in the supergraph,
the \textit{meet-over-all-valid-paths} solution
  $\mvp{\textsf{Env}}(n)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top)$,
where $M_\textsf{Env}$ is extended from edges to paths by composition.

>>>>

The output of the IDE algorithm is, for each node $n$ in the supergraph,
the \textit{meet-over-all-valid-paths} solution
  $\mvp{\textsf{Env}}(n)=\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top)$,\mtodo{Should it be $\Omega$ instead of $\top$?}
where $M_\textsf{Env}$ is extended from edges to paths by composition.
